---
title: "253_project"
author: "Xinyi Wang"
date: "3/26/2021"
output: html_document
---

```{r}
library(caret)
library(ggplot2)
library(dplyr)
library(ISLR)
library(splines)
library(gam)
library(stringr)
library(leaps)
library(rpart.plot)

```

```{r}
airbnb_kaggle <- read.csv("/Users/apple/Downloads/NYC_airbnb_kaggle.csv")
neighbourhood <- read.csv("/Users/apple/Downloads/NYC_nbhd_kaggle.csv")
```

```{r}
set.seed(253)
airbnb <- airbnb_kaggle %>%
  left_join(neighbourhood, c("neighbourhood_cleansed" = "neighbourhood")) %>%
  filter (price < 1000) %>%
  sample_n(5000) %>% 
  select(-id, -host_response_time) %>%
  mutate(host_response_rate = as.numeric(str_remove_all(host_response_rate, "%"))) %>%
  mutate(host_is_superhost = as.logical(toupper(host_is_superhost))) %>%
  mutate(host_has_profile_pic = as.logical(toupper(host_has_profile_pic))) %>%
  mutate(is_location_exact = as.logical(toupper(is_location_exact))) %>%
  mutate(instant_bookable = as.logical(toupper(instant_bookable))) %>%
  mutate(is_business_travel_ready = as.logical(toupper(is_business_travel_ready))) %>%
  mutate(require_guest_profile_picture = as.logical(toupper(require_guest_profile_picture))) %>%
  dplyr::na_if("N/A")
```
```{r}
#airbnb
```
```{r}
airbnb_select <- airbnb %>%
  select(price,property_type,room_type,accommodates,beds,guests_included,minimum_nights,availability_30,bathrooms,bedrooms,review_scores_rating,is_business_travel_ready,cancellation_policy,require_guest_profile_picture,reviews_per_month,neighbourhood_group)
```

Backward selection:

```{r}
ls_mod  <- lm(price~
                   property_type+
                   room_type+
                   accommodates+
                   beds+
                   guests_included+
                   minimum_nights+
                   availability_30+
                   bathrooms+
                   bedrooms+
                   review_scores_rating+
                   is_business_travel_ready+
                   cancellation_policy+
                   require_guest_profile_picture+
                   reviews_per_month+
                   neighbourhood_group, data = airbnb_select)
summary(ls_mod )

```
```{r}
set.seed(253)
ls_mod <- train(
  price~property_type+
                   room_type+
                   accommodates+
                   beds+
                   guests_included+
                   minimum_nights+
                   availability_30+
                   bathrooms+
                   bedrooms+
                   review_scores_rating+
                   is_business_travel_ready+
                   require_guest_profile_picture+
                   reviews_per_month+
                   neighbourhood_group,
    data =airbnb_select ,
    method = "lm",
    trControl = trainControl(method = "cv", number = 10),
    na.action = na.omit
)

ls_mod$results
```


```{r}
set.seed(253)

back_step_mod <- train(
  price~property_type+
                   room_type+
                   accommodates+
                   beds+
                   guests_included+
                   minimum_nights+
                   availability_30+
                   bathrooms+
                   bedrooms+
                   review_scores_rating+
                   is_business_travel_ready+
                   require_guest_profile_picture+
                   reviews_per_month+
                   neighbourhood_group,
    data = airbnb_select,
    method = "leapBackward",
    tuneGrid = data.frame(nvmax = 1:13),
    trControl = trainControl(method = "cv", number = 10),
    metric = "MAE",
    na.action = na.omit
)
summary(back_step_mod)
```

```{r}
plot(back_step_mod)
back_step_mod$results
back_step_mod$results %>% arrange(MAE)
```

```{r}
back_step_mod$bestTune
coef(back_step_mod$finalModel, id = back_step_mod$bestTune$nvmax)
coef(back_step_mod$finalModel, id = 12)
```

LASSO model:
```{r}
set.seed(253)
lasso_mod1 <- train(
    price~property_type+
                   room_type+
                   accommodates+
                   beds+
                   guests_included+
                   minimum_nights+
                   availability_30+
                   bathrooms+
                   bedrooms+
                   review_scores_rating+
                   is_business_travel_ready+
                   require_guest_profile_picture+
                   reviews_per_month+
                   neighbourhood_group,
    data = airbnb_select,
    method = "glmnet",
    trControl = trainControl(method = "cv", number = 10, selectionFunction = "oneSE"),
    tuneGrid = data.frame(alpha = 1, lambda = seq(0, 10, length.out = 100)),
    metric = "MAE",
    na.action = na.omit
)
lasso_mod1$results
```

```{r}
plot(lasso_mod1$finalModel, xvar = "lambda", label = TRUE, col = rainbow(20))
rownames(lasso_mod1$finalModel$beta)
rownames(lasso_mod1$finalModel$beta)[c(2,4)]
```

```{r}
plot(lasso_mod1$finalModel, xvar = "lambda", label = TRUE, col = rainbow(20), ylim = c(-0.5,1))
```

```{r}
plot(lasso_mod1)
```
```{r}
coef(lasso_mod1$finalModel,id = lasso_mod1$bestTune)
```


```{r}
lasso_mod1$bestTune
coef(lasso_mod1$finalModel, id = lasso_mod1$bestTune$lambda)

```

```{r}
coef(back_step_mod$finalModel, id = 12)
back_step_mod$results%>% arrange(MAE)
```

```{r}
coef(lasso_mod1$finalModel, id = 14)
lasso_mod1$results %>% arrange(MAE)
```


Estimate test performance of the models from these different methods. Report and interpret (with units) these estimates along with a measure of uncertainty in the estimate. Compare estimated test performance across methods. Which method(s) might you prefer?

We can observe that backward selection gives us nvmax of 13 with MAE = 46.96494. In contrast, LASSO provides us with nvmax of 14 with MAE = 45.19681. Despite the fact that backward selection has lower nvmax, LASSO's MAE is significantly lower than the MAE of the backward selection. Thus, we prefer LASSO. For backward selection gives us nvmax of 13 with MAE = 46.96494, we can see that MAESD = 3.811582, while for LASSO with nvmax of 14 with MAE = 45.19681, MAESD = 2.535235. The SD of MAE of LASSO is significantly lower. This also shows that LASSO is better.


Compare insights from variable importance analyses from the different methods (stepwise and LASSO, but not OLS). Are there variables for which the methods reach consensus? What insights are expected? Surprising?

We found that the predictor "reviews_per_month" has an coefficient of -4.3496092 is surprising. This shows that with 1 unit increase in monthly review of the house, the price goes down by -4.3496092 in USD.Intuitively, more reviews means more popularity, which, in economics, leads to higher demand. However, with supply holds constant, higher demand doesn't brings higher price. That is kind of counter-intuitive. 

```{r}
lasso_model <- train(data=airbnb_select,
                price~property_type+
                  room_type+
                  ns(accommodates,3)+
                  ns(beds,3)+
                  ns(guests_included,3)+
                  ns(minimum_nights,3)+
                  ns(availability_30,3)+
                  ns(bathrooms,3)+ns(bedrooms,3)+
                  ns(review_scores_rating,3)+
                  is_business_travel_ready+
                  cancellation_policy+
                  require_guest_profile_picture+
                  ns(reviews_per_month,3)+
                  neighbourhood_group,
                method="glmnet",
                trControl=trainControl(method = "cv", number = 10, selectionFunction = "oneSE"),
                metric = "MAE",
                na.action = na.omit)
```

```{r}
lasso_model$results
```

```{r}
coef(lasso_model$finalModel, lasso_model$bestTune$lambda)
```

It has property_type,room_type,accommodates,beds,guests_included,availability_30,bathrooms,bedrooms,review_scores_rating,is_business_travel_readyTRUE,cancellation_policy,require_guest_profile_picture,reviews_per_month,neighbourhood_group as important predictors.

```{r}
full_model <- lm(price ~ property_type+
                  room_type+
                  ns(accommodates,3)+
                  ns(beds,3)+
                  ns(guests_included,3)+
                  ns(minimum_nights,3)+
                  ns(availability_30,3)+
                  ns(bathrooms,3)+ns(bedrooms,3)+
                  ns(review_scores_rating,3)+
                  is_business_travel_ready+
                  cancellation_policy+
                  require_guest_profile_picture+
                  ns(reviews_per_month,3)+
                  neighbourhood_group,data=airbnb_select)
```

```{r}
summary(full_model)$coefficients
```


```{r}
back_step_mod <- train(
    price ~ property_type+
                  room_type+
                  ns(accommodates,3)+
                  ns(beds,3)+
                  ns(guests_included,3)+
                  ns(minimum_nights,3)+
                  ns(availability_30,3)+
                  ns(bathrooms,3)+ns(bedrooms,3)+
                  ns(review_scores_rating,3)+
                  is_business_travel_ready+
                  cancellation_policy+
                  require_guest_profile_picture+
                  ns(reviews_per_month,3)+
                  neighbourhood_group,
    data = airbnb_select,
    method = "leapBackward",
    tuneGrid = data.frame(nvmax = 1:33),
    trControl = trainControl(method = "cv", number =10),
    metric = "MAE",
    na.action = na.omit
)
```

```{r}
summary(back_step_mod)
```

It turend out the the full model is the best.

```{r}
plot(back_step_mod)
```

```{r}
back_step_mod$results
```

```{r}
back_step_mod$results %>% arrange(MAE)
```

```{r}
back_step_mod$bestTune
```

```{r}
coef(back_step_mod$finalModel, id = back_step_mod$bestTune$nvmax)
```
property_type+room_type+accommodates+beds+availability_30+bathrooms+bedrooms+review_scores_rating+is_business_travel_ready+cancellation_policy+require_guest_profile_picture+reviews_per_month+neighbourhood_group
```{r}
airbnb_select_noNA<-tidyr::drop_na(airbnb_select)
back_step_mod_out <- airbnb_select_noNA %>%
    mutate(
        fitted = predict(back_step_mod, newdata = airbnb_select_noNA),
        resid = price - fitted
    )
ggplot(back_step_mod_out, aes(x = fitted, y = resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, color = "red") +
    theme_classic() +
    labs(x = "Fitted values", y = "Residuals")
```

```{r}
airbnb_select <-airbnb_select%>%
  mutate(room_type = str_replace(room_type,"/","_"))%>%
  mutate(property_type=str_replace(property_type," ","_"))%>%
  mutate(property_type=str_replace(property_type,"&","and"))%>%
  mutate(room_type=str_replace(room_type," ","_"))
```

```{r}
airbnb_select
```

```{r}
gam_mod <- train(
    price ~ property_type+room_type+accommodates+beds+availability_30+bathrooms+bedrooms+review_scores_rating+is_business_travel_ready+cancellation_policy+require_guest_profile_picture+reviews_per_month+neighbourhood_group,
    data = airbnb_select,
    method = "gamLoess",
    tuneGrid = data.frame(degree = 1, span = seq(0.5, 0.9, by = 0.1)),
    trControl = trainControl(method = "cv", number = 10, selectionFunction = "best"),
    metric = "MAE",
    na.action = na.omit
)
```

```{r}
plot(gam_mod)
```

```{r}
gam_mod$bestTune
```

```{r}
gam_mod$results
```

```{r}
par(mfrow = c(3,3)) # Sets up a grid of plots
plot(gam_mod$finalModel, se = TRUE)
```


```{r}
set.seed(253)
rf_mod <- train(
      neighbourhood_group ~ 
      property_type+
      price+
      room_type+
      accommodates+
      beds+
      guests_included+
      minimum_nights+
      availability_30+
      bathrooms+
      bedrooms+
      review_scores_rating+
      is_business_travel_ready+
      require_guest_profile_picture+
      reviews_per_month,
    data = airbnb_select,
    method = "rf",
    tuneGrid = data.frame(mtry = c(1,3,7,15)),
    trControl = trainControl(method = "oob", selectionFunction = "best"),
    metric = "Accuracy",
    ntree = 10, 
    na.action = na.omit
)
```

```{r}
rf_mod
```

```{r}
plot(rf_mod)
```


```{r}
rf_mod$finalModel
```

```{r}
var_imp_rf <- randomForest::importance(rf_mod$finalModel)

var_imp_rf <- data.frame(
        predictor = rownames(var_imp_rf),
        MeanDecreaseGini = var_imp_rf[,"MeanDecreaseGini"]
    ) %>%
    arrange(desc(MeanDecreaseGini))

# Top 20
head(var_imp_rf, 7)

# Bottom 10
tail(var_imp_rf, 7)
```

```{r}
ggplot(airbnb_select, aes(x = neighbourhood_group, y = price)) +
    geom_violin()
ggplot(airbnb_select, aes(x = neighbourhood_group, y = reviews_per_month)) +
    geom_violin()
ggplot(airbnb_select, aes(x = neighbourhood_group, y = accommodates)) +
    geom_violin()
ggplot(airbnb_select, aes(x = neighbourhood_group, y = availability_30)) +
    geom_violin()
ggplot(airbnb_select, aes(x = neighbourhood_group, y = review_scores_rating)) +
    geom_violin()
```

```{r}
abnb<-airbnb_select%>%
  filter(neighbourhood_group%in% c("Brooklyn","Manhattan","Queens"))
```

```{r}
tree_mod <- train(
    neighbourhood_group ~ 
      property_type+
      price+
      room_type+
      accommodates+
      beds+
      guests_included+
      minimum_nights+
      availability_30+
      bathrooms+
      bedrooms+
      review_scores_rating+
      is_business_travel_ready+
      require_guest_profile_picture+
      reviews_per_month,
    data = abnb,
    method = "rpart",
    tuneGrid = data.frame(cp = seq(0, 0.0042, length.out = 50)),
    trControl = trainControl(method = "cv", number = 10, selectionFunction = "oneSE"),
    metric = "Accuracy",
    na.action = na.omit
)
rpart.plot(tree_mod$finalModel)
```

```{r}
tree_mod$finalModel$variable.importance
```





